### 2022-10-27 draft/draft.Rmd
fixed typo in theorem 4.2

\begin{theorem}
\label{thm:kcurves-semisupervised}
Let $A \sim \MBM(\{\alpha_1, ..., \alpha_K\}, \{F, ..., F\}, \{g_1, ..., g_K\}; \rho_n)$ such that $F$ has support $[0, 1]$, and each $g_k(t) = g(t; p_k)$ is is a Bezier curve of order $R$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then if $n \rho_n = \omega(\log^{4c} n)$, as $n \to \infty$, the estimates outputted by $K$-curves clustering are such that 
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_n; X) \stackrel{p}{\to} 0,$$
where $L$ is the loss function defined in equation (\ref{eq:kcurves-loss}). 
\end{theorem}

@@

As in the previous setup, we set $n = 128, 256, 512, 1024, 2048$, and we start with completely random initializations as well as initializations in which we know $4$ or $8$ labels from each community. 
For each setting, we simulate 50 replicates. 
Since the curves meet at the origin, we force the fitted Bezier curves to meet at the origin as well by fixing $p_1^{(k)} = (0, 0, 0)$ for each $k$. 
Figure \ref{fig:sim-curves-3} shows the median and interquartile ranges for the error rates for each $n$ and *a priori* known labels per community. 
As in the previous $K = 2$ simulations, the results suggest that for sufficient $n$, we do not benefit from having more known labels, but having a few results in greatly improved performance. Unlike in the previous setup, random initialization results in low community detection error rates, close to the semi-supervised setups.

>>>>

\begin{theorem}
\label{thm:kcurves-semisupervised}
Let $A \sim \MBM(\{\alpha_1, ..., \alpha_K\}, \{F, ..., F\}, \{g_1, ..., g_K\}; \rho_n)$ such that $F$ has support $[0, 1]$, and each $g_k(t) = g(t; p_k)$ is is a Bezier curve of order $R$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then if $n \rho_n = \omega(\log^{4c} n)$, as $n \to \infty$, the estimates outputted by $K$-curves clustering are such that 
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_K; X) \stackrel{p}{\to} 0,$$
where $L$ is the loss function defined in equation (\ref{eq:kcurves-loss}). 
\end{theorem}

@@

As in the previous setup, we set $n = 128, 256, 512, 1024, 2048$, and we started with completely random initializations as well as initializations in which we know $4$ or $8$ labels from each community. 
For each setting, we simulated 50 replicates. 
Since the curves meet at the origin, we forced the fitted Bezier curves to meet at the origin as well by fixing $p_k^{(0)} = (0, 0, 0)$ for each $k$. 
Figure \ref{fig:sim-curves-3} shows the median and interquartile ranges for the error rates for each $n$ and *a priori* known labels per community. 
As in the previous $K = 2$ simulations, the results suggest that for sufficient $n$, we do not benefit from having more known labels, but having a few results in greatly improved performance. Unlike in the previous setup, random initialization results in low community detection error rates, close to the semi-supervised setups for larger $n$.

### 2022-10-27 draft/draft.tex
fixed typo in theorem 4.2

As in the previous setup, we set \(n = 128, 256, 512, 1024, 2048\), and we start with completely random initializations as well as initializations in which we know \(4\) or \(8\) labels from each community.
For each setting, we simulate 50 replicates.
Since the curves meet at the origin, we force the fitted Bezier curves to meet at the origin as well by fixing \(p_1^{(k)} = (0, 0, 0)\) for each \(k\).
Figure \ref{fig:sim-curves-3} shows the median and interquartile ranges for the error rates for each \(n\) and \emph{a priori} known labels per community.
As in the previous \(K = 2\) simulations, the results suggest that for sufficient \(n\), we do not benefit from having more known labels, but having a few results in greatly improved performance. Unlike in the previous setup, random initialization results in low community detection error rates, close to the semi-supervised setups.

>>>>

As in the previous setup, we set \(n = 128, 256, 512, 1024, 2048\), and we started with completely random initializations as well as initializations in which we know \(4\) or \(8\) labels from each community.
For each setting, we simulated 50 replicates.
Since the curves meet at the origin, we forced the fitted Bezier curves to meet at the origin as well by fixing \(p_k^{(0)} = (0, 0, 0)\) for each \(k\).
Figure \ref{fig:sim-curves-3} shows the median and interquartile ranges for the error rates for each \(n\) and \emph{a priori} known labels per community.
As in the previous \(K = 2\) simulations, the results suggest that for sufficient \(n\), we do not benefit from having more known labels, but having a few results in greatly improved performance. Unlike in the previous setup, random initialization results in low community detection error rates, close to the semi-supervised setups for larger \(n\).
